### 2015-05-05 swmpr_manu.tex
almost done with internal revisions, upload tangled script for reproducing figures/tables

% table for retrieval functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Retrieval functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?all\\_params} at the command line).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:retrieve",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Retrieval functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \texttt{?all\_params} at the command line).\label{tab:retrieve}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{all\_params}&Retrieve records starting with the most recent at a given station, all parameters.  Wrapper to \texttt{exportAllParamsXMLNew} function on web services.\tabularnewline
\texttt{all\_params\_dtrng}&Retrieve records of all parameters within a given date range for a station.  Optional argument for a single parameter. Wrapper to \texttt{exportAllParamsDateRangeXMLNew}.\tabularnewline
\texttt{import\_local}&Import files from a local path.  The files must be in a specific format, such as those returned from the \ac{CDMO} using the zip downloads option.\tabularnewline
\texttt{single\_param}&Retrieve records for a single parameter starting with the most recent at a given station.  Wrapper to \texttt{exportSingleParamXMLNew} function on web services.\tabularnewline
\texttt{site\_codes}&Metadata for all stations, wrapper to \texttt{exportStationCodesXMLNew} function on web services.\tabularnewline
\texttt{site\_codes\_ind}&Metadata for all stations at a single site, wrapper  to \texttt{NERRFilterStationCodesXMLNew} function on web services.\tabularnewline
\hline
\end{tabular}\end{center}

@@

% attributes table
%latex.default(to_tab[, -1, drop = F], file = "", caption = "Attributes of a \\texttt{swmpr} object that describe characteristics of the data.  Similar information can be obtained using the \\texttt{str} function.",     rowlabel = "Attributes", colheads = c("Class", "Description"),     rowname = to_tab$Attributes, caption.loc = "top", insert.bottom = foot,     col.just = c("p{0.75in}", "p{3.25in}"), label = "tab:attributes",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Attributes of a \texttt{swmpr} object that describe characteristics of the data.  Similar information can be obtained using the \texttt{str} function.\label{tab:attributes}} 
\begin{center}
\begin{tabular}{lp{0.75in}p{3.25in}}
\hline\hline
\multicolumn{1}{l}{Attributes}&\multicolumn{1}{c}{Class}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{names}&character&Column names of the entire data set, inherited from the \texttt{data.frame} object class\tabularnewline
\texttt{row.names}&integer&Row names of the data set, inherited from the \texttt{data.frame} object class\tabularnewline
\texttt{class}&character&Class of the data object indicating \texttt{swmpr} and \texttt{data.frame}\tabularnewline
\texttt{station}&character&Station identifier used by \ac{NERRS} as a string with 7 or 8 characters\tabularnewline
\texttt{parameters}&character&Character vector of column names for data parameters, e.g., \texttt{`do\_mgl'}\tabularnewline
\texttt{qaqc\_cols}&logical&Indicates if \ac{QAQC} columns are present in the raw data\tabularnewline
\texttt{date\_rng}&POSIXct&Start and end dates for the raw data\tabularnewline
\texttt{timezone}&character&Timezone of the station using the city/country format\textsuperscript{\textit{a}}\tabularnewline
\texttt{stamp\_class}&character&Class of the \texttt{datetimestamp} column, usually POSIXct unless data have been aggregated\tabularnewline
\hline
\end{tabular}\end{center}

\textsuperscript{\textit{a}}\footnotesize Time zones that do not observe daylight savings are used for \texttt{swmpr} objects and may not be cities in the United States.  For example, ``America/Jamaica" is the same as Eastern Standard Time.\end{table}

@@

% table for organize functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Organizing functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?comb} at the command line).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:organize",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Organizing functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \texttt{?comb} at the command line).\label{tab:organize}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{comb}&Combines \texttt{swmpr} objects to a common time series using setstep, such as combining the weather, nutrients, and water quality data for a single station. Only different data types can be combined.\tabularnewline
\texttt{qaqc}&Remove \ac{QAQC} columns and remove data based on \ac{QAQC} flag values for a \texttt{swmpr} object.  Only applies if \ac{QAQC} columns are present. \tabularnewline
\texttt{qaqcchk}&View a summary of the number of observations in a \texttt{swmpr} object that are assigned to different \ac{QAQC} flags used by \ac{CDMO}.  The output can be used to inform further processing.\tabularnewline
\texttt{rem\_reps}&Remove replicate nutrient data that occur on the same day.  The default is to average replicates.\tabularnewline
\texttt{setstep}&Format data from a \texttt{swmpr} object to a continuous time series at a given timestep.  The function is used in \texttt{comb} and can also be used with individual stations.\tabularnewline
\texttt{subset}&Subset by dates and/or columns for a \texttt{swmpr} object.  This is a method passed to the generic \texttt{subset} function provided in the base package.\tabularnewline
\hline
\end{tabular}\end{center}

@@

The \texttt{aggreswmp} function aggregates parameter data for a \texttt{swmpr} object by set units of time.  This function is most useful for aggregating noisy data to evaluate trends on longer time scales or to simply reduce the size of a dataset.  Data can be aggregated by years, quarters, months, weeks, days, or hours by a predefined function, which defaults to the mean.  A \texttt{swmpr} object is returned for the aggregated data, although the \texttt{datetimestamp} vector will be converted to a date object if the aggregation period is a day or longer.  Days are assigned to the date vector if the aggregation period is a week or longer based on the \texttt{round} method for IDate objects created in the data.table package \cite{Dowle14}.  Additionally, the method of treating \texttt{NA} values for the aggregation function should be noted since this may greatly affect the quantity of data that are returned, particularly for nutrient data.

% table for analysis functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Analysis functions available from the SWMPr package.  Full documentation for each function is in the help file (e.g., execute \\texttt{?aggreswmp} at the command line).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:analyze",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Analysis functions available from the SWMPr package.  Full documentation for each function is in the help file (e.g., execute \texttt{?aggreswmp} at the command line).\label{tab:analyze}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{aggreswmp}&Aggregate \texttt{swmpr} objects for different time periods - years, quarters, months,  weeks, days, or hours.  The aggregation function defaults to the mean.\tabularnewline
\texttt{aggremetab}&Aggregate metabolism data from a \texttt{swmpr} object.  This is primarly used within \texttt{plot\_metab} but may be useful for simple summaries of raw metabolism data.\tabularnewline
\texttt{ecometab}&Estimate ecosystem metabolism for a combined water quality and weather dataset using the open-water method.\tabularnewline
\texttt{decomp}&Decompose a \texttt{swmpr} time series into trend, seasonal, and residual components.  This is a simple wrapper to \texttt{decompose} \cite{Kendall83}.  Decomposition of monthly or daily trends is possible.\tabularnewline
\texttt{decomp\_cj}&Decompose a \texttt{swmpr} time series into grandmean, annual, seasonal, and events components.  This is a simple wrapper to \texttt{decompTs} in the wq package \cite{Jassby14}.  Only monthly decomposition is possible.\tabularnewline
\texttt{hist}&Plot a histogram for a \texttt{swmpr} object.\tabularnewline
\texttt{lines}&Add lines to an existing plot created with \texttt{plot}.\tabularnewline
\texttt{na.approx}&Linearly interpolate missing data (\texttt{NA} values) in a \texttt{swmpr} object. The maximum gap size that is interpolated is defined by the arguments.\tabularnewline
\texttt{plot}&Plot a univariate  time series for a \texttt{swmpr} object.  The parameter name must be specified.\tabularnewline
\texttt{plot\_metab}&Plot ecosystem metabolism estimates after running \texttt{ecometab} on a \texttt{swmpr} object.\tabularnewline
\texttt{plot\_summary}&Create summary plots of seasonal/annual trends and anomalies for a water a single paramter of interest.\tabularnewline
\texttt{smoother}&Smooth \texttt{swmpr} objects with a moving window average.  Window size and sides (e.g., centered) can be specified, passed to \texttt{filter}.\tabularnewline
\hline
\end{tabular}\end{center}

@@

\begin{knitrout}\small
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
> # get data
> data(apacpwq)
> dat <- qaqc(apacpwq)
> 
> # get mean DO by months
> aggreswmp(dat, 'months', params = c('do_mgl'))
\end{verbatim}
\end{kframe}
\end{knitrout}

Time series can be smoothed to better characterize a signal independent of noise (\Cref{fig:smooth_ex}).  Although there are many approaches to smoothing, a moving window average is intuitive and commonly used.  The \texttt{smoother} function can be used to smooth parameters in a \texttt{swmpr} object using a specified window size with arguments passed to the \texttt{filter} function from the base installation.  The \texttt{window} argument specifies the number of observations included in the moving average where larger windows result in greater smoothing.  The \texttt{sides} argument specifies how the average is calculated for each observation.  Setting \texttt{sides = 1} will filter observations within the window that are previous to the current observation, whereas \texttt{sides = 2} will filter observations within the window centered at zero lag from the current observation. As before, the \texttt{params} argument specifies which parameters to smooth.

@@

% table for misc functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Miscellaneous functions available from the SWMPr package.  Most are used within the main functions above but may be useful for customized evaluations of \\ac{SWMP} data.  Full documentation for each function is in the help file (e.g., execute \\texttt{?calckl} at the command line).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:misc",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Miscellaneous functions available from the SWMPr package.  Most are used within the main functions above but may be useful for customized evaluations of \ac{SWMP} data.  Full documentation for each function is in the help file (e.g., execute \texttt{?calckl} at the command line).\label{tab:misc}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{calckl}&Estimate the reaeration coefficient for air-sea gas exchange.  Used in the \texttt{ecometab} function.\tabularnewline
\texttt{map\_reserve}&Create a map of all stations in a reserve using the ggmap package.\tabularnewline
\texttt{metab\_day}&Identify the metabolic day for each approximate 24 period in an hourly time series.  Used in the \texttt{ecometab} function.\tabularnewline
\texttt{param\_names}&Returns column names as a list for the parameter types (nutrients, weather, or water quality).  Includes \ac{QAQC} columns with \texttt{f\_} prefix. Used in the data retrieval functions.\tabularnewline
\texttt{parser}&Parses HTML returned from \ac{CDMO} data requests.  Used in the retrieval functions.\tabularnewline
\texttt{swmpr}&Creates a \texttt{swmpr} object class.  Used in the data retrieval functions.\tabularnewline
\texttt{time\_vec}&Converts time vectors to \texttt{POSIXct} objects with the appropriate time zone for a site.  Used in the data retrieval functions.\tabularnewline
\hline
\end{tabular}\end{center}

For brevity, only the \texttt{reserve\_map} function is discussed.  This function can be used to create a map with all stations at a reserve using functions in the ggmap package \cite{Kahle13}. The current function is limited to Google maps of four types that can be set with the \texttt{map\_type} argument: terrain (default), satellite, roadmap, or hybrid.  The \texttt{zoom} argument may have to be chosen through trial and error depending on the spatial extent of the reserve.  See the help documentation for the \texttt{ggmap} function for more info on \texttt{zoom}.

@@

>>>>

% table for retrieval functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Retrieval functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?all\\_params} for individual functions or \\texttt{help.search(`retrieve', package = `SWMPr')} for all).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:retrieve",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Retrieval functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \texttt{?all\_params} for individual functions or \texttt{help.search(`retrieve', package = `SWMPr')} for all).\label{tab:retrieve}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{all\_params}&Retrieve records starting with the most recent at a given station, all parameters.  Wrapper to \texttt{exportAllParamsXMLNew} function on web services.\tabularnewline
\texttt{all\_params\_dtrng}&Retrieve records of all parameters within a given date range for a station.  Optional argument for a single parameter. Wrapper to \texttt{exportAllParamsDateRangeXMLNew}.\tabularnewline
\texttt{import\_local}&Import files from a local path.  The files must be in a specific format, such as those returned from the \ac{CDMO} using the zip downloads option.\tabularnewline
\texttt{single\_param}&Retrieve records for a single parameter starting with the most recent at a given station.  Wrapper to \texttt{exportSingleParamXMLNew} function on web services.\tabularnewline
\texttt{site\_codes}&Metadata for all stations, wrapper to \texttt{exportStationCodesXMLNew} function on web services.\tabularnewline
\texttt{site\_codes\_ind}&Metadata for all stations at a single site, wrapper  to \texttt{NERRFilterStationCodesXMLNew} function on web services.\tabularnewline
\hline
\end{tabular}\end{center}

@@

% attributes table
%latex.default(to_tab[, -1, drop = F], file = "", caption = "Attributes of a \\texttt{swmpr} object that describe characteristics of the data.",     rowlabel = "Attributes", colheads = c("Class", "Description"),     rowname = to_tab$Attributes, caption.loc = "top", insert.bottom = foot,     col.just = c("p{0.75in}", "p{3.25in}"), label = "tab:attributes",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Attributes of a \texttt{swmpr} object that describe characteristics of the data.\label{tab:attributes}} 
\begin{center}
\begin{tabular}{lp{0.75in}p{3.25in}}
\hline\hline
\multicolumn{1}{l}{Attributes}&\multicolumn{1}{c}{Class}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{names}&character&Column names of the entire data set, inherited from the \texttt{data.frame} object class\tabularnewline
\texttt{row.names}&integer&Row names of the data set, inherited from the \texttt{data.frame} object class\tabularnewline
\texttt{class}&character&Class of the data object indicating \texttt{swmpr} and \texttt{data.frame}\tabularnewline
\texttt{station}&character&Station identifier used by \ac{NERRS} as a string with 7 or 8 characters\tabularnewline
\texttt{parameters}&character&Character vector of column names for data parameters, e.g., \texttt{`do\_mgl'}\tabularnewline
\texttt{qaqc\_cols}&logical&Indicates if \ac{QAQC} columns are present in the raw data\tabularnewline
\texttt{date\_rng}&POSIXct&Start and end dates for the raw data\tabularnewline
\texttt{timezone}&character&Timezone of the station using the city/country format\textsuperscript{\textit{a}}\tabularnewline
\texttt{stamp\_class}&character&Class of the \texttt{datetimestamp} column, usually POSIXct unless data have been aggregated\tabularnewline
\hline
\end{tabular}\end{center}

\textsuperscript{\textit{a}}\footnotesize Time zones that do not observe daylight savings are used for \texttt{swmpr} objects and may not be cities in the United States.  For example, ``America/Jamaica" is used for Eastern Standard Time.\end{table}

@@

% table for organize functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Organizing functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \\texttt{?comb} for individual functions or \\texttt{help.search(`organize', package = `SWMPr')} for all).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:organize",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Organizing functions available from the SWMPr package. Full documentation for each function is in the help file (e.g., execute \texttt{?comb} for individual functions or \texttt{help.search(`organize', package = `SWMPr')} for all).\label{tab:organize}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{comb}&Combines \texttt{swmpr} objects to a common time series using setstep, such as combining the weather, nutrients, and water quality data for a single station. Only different data types can be combined.\tabularnewline
\texttt{qaqc}&Remove \ac{QAQC} columns and remove data based on \ac{QAQC} flag values for a \texttt{swmpr} object.  Only applies if \ac{QAQC} columns are present. \tabularnewline
\texttt{qaqcchk}&View a summary of the number of observations in a \texttt{swmpr} object that are assigned to different \ac{QAQC} flags used by \ac{CDMO}.  The output can be used to inform further processing.\tabularnewline
\texttt{rem\_reps}&Remove replicate nutrient data that occur on the same day.  The default is to average replicates.\tabularnewline
\texttt{setstep}&Format data from a \texttt{swmpr} object to a continuous time series at a given timestep.  The function is used in \texttt{comb} and can also be used with individual stations.\tabularnewline
\texttt{subset}&Subset by dates and/or columns for a \texttt{swmpr} object.  This is a method passed to the generic \texttt{subset} function provided in the base package.\tabularnewline
\hline
\end{tabular}\end{center}

@@

The \texttt{aggreswmp} function aggregates parameter data for a \texttt{swmpr} object by set units of time.  This function is most useful for aggregating noisy data to evaluate trends on longer time scales or to simply reduce the size of a dataset.  Data can be aggregated by years, quarters, months, weeks, days, or hours by a predefined function, which defaults to the mean.  A \texttt{swmpr} object is returned for the aggregated data, although the \texttt{datetimestamp} vector will be converted to a date object if the aggregation period is a day or longer.  Days are assigned to the date vector if the aggregation period is a week or longer based on the \texttt{round} method for IDate objects created in the data.table package \cite{Dowle14}.  Additionally, the method of treating \texttt{NA} values for the aggregation function should be noted since this may greatly affect the quantity of data that are returned, particularly for nutrient data (see the example below).

% table for analysis functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Analysis functions available from the SWMPr package.  Full documentation for each function is in the help file (e.g., execute \\texttt{?aggreswmp} for individual functions or \\texttt{help.search(`analyze', package = `SWMPr')} for all).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:analyze",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Analysis functions available from the SWMPr package.  Full documentation for each function is in the help file (e.g., execute \texttt{?aggreswmp} for individual functions or \texttt{help.search(`analyze', package = `SWMPr')} for all).\label{tab:analyze}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{aggreswmp}&Aggregate \texttt{swmpr} objects for different time periods - years, quarters, months,  weeks, days, or hours.  The aggregation function defaults to the mean.\tabularnewline
\texttt{aggremetab}&Aggregate metabolism data from a \texttt{swmpr} object.  This is primarly used within \texttt{plot\_metab} but may be useful for simple summaries of raw metabolism data.\tabularnewline
\texttt{ecometab}&Estimate ecosystem metabolism for a combined water quality and weather dataset using the open-water method.\tabularnewline
\texttt{decomp}&Decompose a \texttt{swmpr} time series into trend, seasonal, and residual components.  This is a simple wrapper to \texttt{decompose} \cite{Kendall83}.  Decomposition of monthly or daily trends is possible.\tabularnewline
\texttt{decomp\_cj}&Decompose a \texttt{swmpr} time series into grandmean, annual, seasonal, and events components.  This is a simple wrapper to \texttt{decompTs} in the wq package \cite{Jassby14}.  Only monthly decomposition is possible.\tabularnewline
\texttt{hist}&Plot a histogram for a \texttt{swmpr} object.\tabularnewline
\texttt{lines}&Add lines to an existing plot created with \texttt{plot}.\tabularnewline
\texttt{map\_reserve}&Create a map of all stations in a reserve using the ggmap package.\tabularnewline
\texttt{na.approx}&Linearly interpolate missing data (\texttt{NA} values) in a \texttt{swmpr} object. The maximum gap size that is interpolated is defined by the arguments.\tabularnewline
\texttt{plot}&Plot a univariate  time series for a \texttt{swmpr} object.  The parameter name must be specified.\tabularnewline
\texttt{plot\_metab}&Plot ecosystem metabolism estimates after running \texttt{ecometab} on a \texttt{swmpr} object.\tabularnewline
\texttt{plot\_summary}&Create summary plots of seasonal/annual trends and anomalies for a water a single paramter of interest.\tabularnewline
\texttt{smoother}&Smooth \texttt{swmpr} objects with a moving window average.  Window size and sides (e.g., centered) can be specified, passed to \texttt{filter}.\tabularnewline
\hline
\end{tabular}\end{center}

@@

\begin{knitrout}\small
\definecolor{shadecolor}{rgb}{1, 1, 1}\color{fgcolor}\begin{kframe}
\begin{verbatim}
> # get data, keep all observations
> data(apacpnut)
> dat <- qaqc(apacpnut, qaqc_keep = NULL)
> 
> # aggregate by quarters
> agg_dat <- aggreswmp(dat, by = 'quarters')
> nrow(agg_dat)
## [1] 47
> # aggregate by quarters, remove rows with NA values
> # note the reduction in the number of rows
> agg_dat2 <- aggreswmp(dat, by = 'quarters', na.action = na.omit)
> nrow(agg_dat2)
## [1] 16
\end{verbatim}
\end{kframe}
\end{knitrout}

Time series can be smoothed to better characterize a signal from noisy data (\Cref{fig:smooth_ex}).  Although there are many approaches to smoothing, a moving window average is intuitive and commonly used.  The \texttt{smoother} function can be used to smooth parameters in a \texttt{swmpr} object using a specified window size.  The \texttt{window} argument specifies the number of observations included in the moving average where larger windows result in greater smoothing.  The \texttt{sides} argument specifies how the average is calculated for each observation.  Setting \texttt{sides = 1} will filter observations within the window that are previous to the current observation, whereas \texttt{sides = 2} will filter observations within the window centered at zero lag from the current observation. As before, the \texttt{params} argument specifies which parameters to smooth.

@@

Finally, the \texttt{map\_reserve} function can be used to create a map with all stations at a reserve using functions in the ggmap package \cite{Kahle13}. This map may be useful for aiding the interpretation of spatial trends in water quality parameters given the relative locations in a reserve.  The current function is limited to Google maps of four types that can be set with the \texttt{map\_type} argument: terrain (default), satellite, roadmap, or hybrid.  The \texttt{zoom} argument can be chosen through trial and error depending on the spatial extent of the reserve.  See the help documentation for the \texttt{ggmap} function for more info on \texttt{zoom}.

@@

% table for misc functions
%latex.default(to_tab[, "Description", drop = F], file = "", caption = "Miscellaneous functions available from the SWMPr package.  Most are used within the main functions above but may be useful for customized evaluations of \\ac{SWMP} data.  Full documentation for each function is in the help file (e.g., execute \\texttt{?calckl} at the command line).",     rowlabel = "Function", colheads = "Description", rowname = to_tab$Functions,     caption.loc = "top", col.just = c("p{3.5in}"), label = "tab:misc",     table.env = FALSE)%
\begin{table}[!tbp]
\caption{Miscellaneous functions available from the SWMPr package.  Most are used within the main functions above but may be useful for customized evaluations of \ac{SWMP} data.  Full documentation for each function is in the help file (e.g., execute \texttt{?calckl} at the command line).\label{tab:misc}} 
\begin{center}
\begin{tabular}{lp{3.5in}}
\hline\hline
\multicolumn{1}{l}{Function}&\multicolumn{1}{c}{Description}\tabularnewline
\hline
\texttt{calckl}&Estimate the reaeration coefficient for air-sea gas exchange.  Used in the \texttt{ecometab} function.\tabularnewline
\texttt{metab\_day}&Identify the metabolic day for each approximate 24 period in an hourly time series.  Used in the \texttt{ecometab} function.\tabularnewline
\texttt{param\_names}&Returns column names as a list for the parameter types (nutrients, weather, or water quality).  Includes \ac{QAQC} columns with \texttt{f\_} prefix. Used in the data retrieval functions.\tabularnewline
\texttt{parser}&Parses HTML returned from \ac{CDMO} data requests.  Used in the retrieval functions.\tabularnewline
\texttt{swmpr}&Creates a \texttt{swmpr} object class.  Used in the data retrieval functions.\tabularnewline
\texttt{time\_vec}&Converts time vectors to \texttt{POSIXct} objects with the appropriate time zone for a site.  Used in the data retrieval functions.\tabularnewline
\hline
\end{tabular}\end{center}
